Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Nits

The paper is structured as follows.  It first starts with a background
section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key
contributions:
\begin{itemize}

@@

To understand \sys better under a realistic workload, we use a large pipeline inspired by the introductory program of Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}.
At a high level, the goal is to process multi-year weather data from NCDC to identify the temperature over the past several years.
The original task, as presented in the book, can be thought of comprising three sub-tasks:
  download weather data from NCDC (shell), convert them to a format that is Hadoop-friendly (shell), and process them to identify the maximum temperature (Hadoop).
Only the last of these tasks is the real focus of the chapter, demonstrate the benefits of using distributed analytics system such as Hadoop.

@@

A less obvious take-away from this case was that large, complex pipelines enable significant freedom in how to express their stages.
Several stages in the original shell program (taken from the book) are expressed as a single \ttt{awk} script;
  unfortunately, \ttt{awk} is too general to have a meaningful distributability signature.
A much simpler pipeline that builds on built-in \unix primitives is trivially distributable, 
  but might not perform as well in the centralized case.
% For example, the \ttt{sort} command at the end is an expensive version of extracting the maximum element;
%   this could have been expressed with a simple \ttt{awk} script that only keeps track of the max.

>>>>

The paper is structured as follows.  It starts with a background
section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key
contributions:
\begin{itemize}

@@

To understand \sys better under a realistic workload, we use a large pipeline inspired by the introductory program of Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}.
At a high level, the goal is to process multi-year weather data from NCDC to identify the maximum temperature over the past several years.
The original task, as presented in the book, can be thought of comprising three sub-tasks:
  download weather data from NCDC (shell), convert them to a format that is Hadoop-friendly (shell), and process them to identify the maximum temperature (Hadoop).
Only the last of these tasks is the real focus of the chapter, demonstrate the benefits of using distributed analytics system such as Hadoop.

@@

A less obvious take-away from this case is that large, complex pipelines enable significant freedom in how to express their stages.
Several stages in the original shell program (taken from the book) are expressed as a single \ttt{awk} script;
  unfortunately, \ttt{awk} is too general to have a meaningful distributability signature.
A much simpler pipeline that builds on built-in \unix primitives is trivially distributable, 
  but might not perform as well in the centralized case.
% For example, the \ttt{sort} command at the end is an expensive version of extracting the maximum element;
%   this could have been expressed with a simple \ttt{awk} script that only keeps track of the max.
